---
title: "Skimr"
format: html
author: "Nathan & Bhuvan"
---

# Note
### the following chunk is not included within the library and is only used for datasets to demonstrate the effectiveness.
```{r}
dataset<- read.csv('student_habits_performance.csv')

library("primes")
vector<- c(generate_primes(1, 10000000))
```



#Installation
```{r}
install.packages("skimr", dep=TRUE)
library("skimr")
```

#Use cases
###Skimming a dataset and gives the variable types

##For Characters
### it gives the max and min character length and how many unique observations each variable has

##For Numeric
### it shows the mean, standard deviation, and the quartiles.
```{r}
skim(dataset)
```

#Unique function
### The unique function tells you how many unique variables there are currently in the vector "vector" there are 664587 observations, which are all unique.

```{r}
vector<- c(vector, 1, 3, 2,10)
n_unique(vector)

```
### After adding 1 and 3 it now lowers the count of how many unique observations there are.


#Finding max/min character length

```{r}
max(vector)
max_char(vector)

min_char(vector)
```

